An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-08 mixedwindow.tex
Set Pi = 1 in theory and simulations
Setting Pi = 1 should give essentially the same performance, but makes
the expression for the OOS statistic marginally simpler.

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \oavg{t}
  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
  \end{equation*}
  and $\hat g_t = g_t(\hat\beta_t)$.
\end{thm}

@@

\begin{rem}
  As in \citet{Wes:96}, $\Pi \to 1$ as $T \to \infty$ since $R$ is
  fixed.  But using West's general formula for $\Pi$ (which holds when
  $\lim \tfrac{P}{R} \in [0,\infty]$) can improve the statistic in practice,
  since researchers often invoke ``fixed $R$'' asymptotics when $R$ is
  large.  Section~\ref{sec:2} shows via Monte Carlo that this
  approximation can be accurate even when $R$ and $P$ are equal.
\end{rem}

>>>>

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
  \end{align*}
  $\bar{g} = \oavg{t}
  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
  \end{equation*}
  and $\hat g_t = g_t(\hat\beta_t)$.
\end{thm}

@@
